Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-08-02 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Load data from packages in first code chunk

#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
library(countyweather)
```

@@

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Vector of all storms in study.
data("closest_dist")
storms <- unique(closest_dist$storm_id)
storms <- storms[which(gsub("*.+-", "", storms) <= 2011)]
```

@@

```{r warning = FALSE, message = FALSE, echo = FALSE}
data(closest_dist)

# Generate a list of unique study fips (all in the eastern US)
my_fips <- closest_dist$fips
my_fips <- unique(my_fips)
storm_lag <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 150, dist_limit = 500,
                             days_include = -5:3)
storm_lag <- storm_lag %>%
        mutate(storm_county = paste0(storm_id, "_", fips))
data(rain)
rain_lag <- rain %>%
        mutate(storm_county = paste0(storm_id, "_", fips)) %>%
        filter(storm_county %in% storm_lag$storm_county) %>%
        group_by(storm_county) %>%
        mutate(cumulative_rain = cumsum(precip),
               difference_rain = lead(cumulative_rain) - cumulative_rain,
               next_lag = lead(lag),
               next_cumulative_rain = lead(cumulative_rain),
               most_rain = difference_rain == max(difference_rain,
                                                  na.rm = TRUE),
               over_50 = lead(precip) > 50)
to_highlight <- data.frame(x = c(-3.1, -3.1, 1.1, 1.1), y = c(0, 500, 500, 0))

@@

```{r eval = FALSE}
county_timeseries(fips = ike_fips[1:2], 
                  percent_coverage = 0, 
                  date_min = "2008-09-01", 
                  date_max = "2010-09-14", var = "PRCP", 
                  out_directory = "ike_ex")
data("closest_dist")
data(rain)
ike_1 <- readRDS("ike_ex/12021.rds")
keys_cd <- subset(closest_dist, closest_dist$storm_id == "Ike-2008" & closest_dist$fips == "12087")
keys_cd <- keys_cd$closest_date
ike_1 <- ike_1 %>%
        select(date, prcp) %>%
        filter(date %in% seq(from = as.Date("2008-09-07"), to = as.Date("2008-09-10"), by = 1))
ike_rain <- subset(rain, rain$storm_id == "Ike-2008" & rain$fips == "12087")
ike_sum <- sum(ike_1$prcp)
ike_nldas_sum <- subset(ike_nldas, ike_nldas$fips == "12087")
ike_nldas_sum <- ike_nldas_sum$tot_precip
```

@@

```{r echo = FALSE}
data(closest_dist)

# Generate a list of unique study fips (all in the eastern US)
my_fips <- closest_dist$fips
my_fips <- unique(my_fips)

@@

```{r echo = FALSE, warning=FALSE, message=FALSE}
data(closest_dist)

# Generate a list of unique study fips (all in the eastern US)
my_fips <- closest_dist$fips
my_fips <- unique(my_fips)

@@

```{r echo = FALSE, message = FALSE, warning = FALSE}
data("closest_dist")
all_counties <- unique(closest_dist$fips)

>>>>

#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
library(countyweather)

data(closest_dist)
data(rain)
```

@@

```{r echo = FALSE, message = FALSE, warning = FALSE}
# Vector of all storms in study.

storms <- unique(closest_dist$storm_id)
storms <- storms[which(gsub("*.+-", "", storms) <= 2011)]
```

@@

```{r warning = FALSE, message = FALSE, echo = FALSE}
# Generate a list of unique study fips (all in the eastern US)
my_fips <- closest_dist$fips
my_fips <- unique(my_fips)
storm_lag <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 150, dist_limit = 500,
                             days_include = -5:3)
storm_lag <- storm_lag %>%
        mutate(storm_county = paste0(storm_id, "_", fips))

rain_lag <- rain %>%
        mutate(storm_county = paste0(storm_id, "_", fips)) %>%
        filter(storm_county %in% storm_lag$storm_county) %>%
        group_by(storm_county) %>%
        mutate(cumulative_rain = cumsum(precip),
               difference_rain = lead(cumulative_rain) - cumulative_rain,
               next_lag = lead(lag),
               next_cumulative_rain = lead(cumulative_rain),
               most_rain = difference_rain == max(difference_rain,
                                                  na.rm = TRUE),
               over_50 = lead(precip) > 50)
to_highlight <- data.frame(x = c(-3.1, -3.1, 1.1, 1.1), y = c(0, 500, 500, 0))

@@

```{r eval = FALSE}
county_timeseries(fips = ike_fips[1:2], 
                  percent_coverage = 0, 
                  date_min = "2008-09-01", 
                  date_max = "2010-09-14", var = "PRCP", 
                  out_directory = "ike_ex")
ike_1 <- readRDS("ike_ex/12021.rds")
keys_cd <- subset(closest_dist, closest_dist$storm_id == "Ike-2008" & closest_dist$fips == "12087")
keys_cd <- keys_cd$closest_date
ike_1 <- ike_1 %>%
        select(date, prcp) %>%
        filter(date %in% seq(from = as.Date("2008-09-07"), to = as.Date("2008-09-10"), by = 1))
ike_rain <- subset(rain, rain$storm_id == "Ike-2008" & rain$fips == "12087")
ike_sum <- sum(ike_1$prcp)
ike_nldas_sum <- subset(ike_nldas, ike_nldas$fips == "12087")
ike_nldas_sum <- ike_nldas_sum$tot_precip
```

@@

```{r echo = FALSE}
# Generate a list of unique study fips (all in the eastern US)
my_fips <- closest_dist$fips
my_fips <- unique(my_fips)

@@

```{r echo = FALSE, warning=FALSE, message=FALSE}
# Generate a list of unique study fips (all in the eastern US)
my_fips <- closest_dist$fips
my_fips <- unique(my_fips)

@@

```{r echo = FALSE, message = FALSE, warning = FALSE}
all_counties <- unique(closest_dist$fips)
